Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-03-20 paper/Paper.Rnw
commits I should have made a couple weeks ago

%***DAN: This para will likely have to be revised depending on how Jasmin revises the diatom figure presentation
To display results for goal G3, we plotted the terms of (\ref{eq:full_decomp}) against one of the parameters 
$\theta_0$, $a$ and $P$ at a time, while keeping the other two fixed at the values
used by \cite{Descamps_2005}. We also generated two-dimensional plots, where
two of the parameters $\theta_0$, $a$ and $P$ were varied and the third was kept fixed
at the value used by \cite{Descamps_2005}. For the two-dimensional plots, the quantity  
$\Delta_i^{[EC]}/\text{GWR}$ was displayed using color, to convey the 
importance of the ATA contribution relative to the whole GWR. Larger magnitudes
of this quantity indicate greater importance of ATAs. The case
$\Delta_i^{[EC]}>\text{GWR}>0$ (which produces $\Delta_i^{[EC]}/\text{GWR}>1$)
corresponds to ATA rescue, and the case $\Delta_i^{[EC]}<\text{GWR}<0$
(which also produces $\Delta_i^{[EC]}/\text{GWR}>1$) corresponds to ATA exclusion.
Thus the condition $\Delta_i^{[EC]}/\text{GWR}>1$ encompasses the cases for which ATA
exclusion or rescue occurred, though the condition does not delineate, by itself,
which of these was the case.

@@

%G4 ***DAN: Dan, this will have to be edited after Jasmin gets done editing the corresponding figures
Fulfilling goal G3 of the Introduction (to provide an empirical example of species coexistence 
which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that ATA contributions to coexistence often have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition (Fig. \ref{fig:fig5}), and that 
ATA rescue occurs for many combinations of parameters for this system (Fig. \ref{fig:fig5},
but especially Fig. \ref{fig:fig6}).

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig5.pdf}
\caption{The contribution of ATAs to GWR of \emph{F. crotonensis}
in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
other components of the MCT decomposition. All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). 
For each panel, 
two of the three parameters defining the temperature oscillation (the amplitude, $a$; period, $P$; 
and mean, $\theta_0$; see Methods) were fixed at the values used by 
\cite{Descamps_2005} ($a=6^\circ$C, $P=60$d, $\theta_0=18^\circ$C), and 
GWR and components of the MCT decomposition
were then plotted against the third parameter. The original values of the varying parameters 
are indicated by vertical dashed magenta lines. ATA contributions 
had magnitude comparable to other components, 
indicating that ATAs can contribute meaningfully
to diatom coexistence in this system. In some instances, the GWR line (orange) falls 
between the ATA line (red)
and the horizontal axis, indicating that, for those parameter values, ATAs make the difference between species
coexistence and exclusion of \emph{F. crotonensis}. 
Standard errors of plotted quantities were always less then \Sexpr{round(se5,5)}, so are not shown.
For the parameters we considered, GWR of the other species, \emph{C. pseudostelligera}, 
was always positive both including and
excluding the effects of ATAs, so GWR for \emph{F. crotonensis}, decomposed here, is a 
sufficient coexistence metric.}  \label{fig:fig5}
\end{figure}

\begin{figure}
\includegraphics[width=.38\textwidth]{../results_figs/fig6.pdf}
\caption{The contribution of ATAs to GWR of \emph{F. crotonensis}
in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
the GWR itself. The ratio $\Delta_i^{[EC]}/\text{GWR}$ is shown, larger magnitudes
indicating greater importance of ATAs and values greater than $1$ corresponding to either
ATA rescue or ATA exclusion (Methods). For this system and the plotted parameters, 
$\Delta_i^{[EC]}$ was always positive, so cyan indicates exclusion of \emph{F. crotonensis} and
magenta indicates coexistence of the two diatom species. Values greater than 1 or less than -1
were remapped to 1 and -1, respectively, for readability.
For the parameters we considered, GWR of the other species, \emph{C. pseudostelligera}, was always positive both including and
excluding ATAs, so GWR for \emph{F. crotonensis} is a sufficient coexistence metric.
Standard errors of plotted quantities were always less then \Sexpr{round(se6,5)}, so are not shown.} \label{fig:fig6}
\end{figure}

>>>>

%One-parameters plots
To display results for goal G3, we started by plotting the terms of 
(\ref{eq:full_decomp}) against one of the parameters 
$\theta_0$, $a$ and $P$ at a time, while keeping the other two fixed at the values
used by \cite{Descamps_2005}. We again labelled regions of parameters space corresponding to
ATA rescue or exclusion.

%Two-parameter plots
%***DAN: This para will likely have to be revised depending on how Jasmin revises the diatom figure presentation
We also generated two-dimensional plots, where
two of the parameters $\theta_0$, $a$ and $P$ were varied and the third was kept fixed
at the value used by \cite{Descamps_2005}. For the two-dimensional plots, the quantity  
$\Delta_i^{[EC]}/\text{GWR}$ was displayed using color, to convey the 
importance of the ATA contribution relative to the whole GWR. Larger magnitudes
of this quantity indicate greater importance of ATAs. The case
$\Delta_i^{[EC]}>\text{GWR}>0$ (which produces $\Delta_i^{[EC]}/\text{GWR}>1$)
corresponds to ATA rescue, and the case $\Delta_i^{[EC]}<\text{GWR}<0$
(which also produces $\Delta_i^{[EC]}/\text{GWR}>1$) corresponds to ATA exclusion.
Thus the condition $\Delta_i^{[EC]}/\text{GWR}>1$ encompasses the cases for which ATA
exclusion or rescue occurred, though the condition does not delineate, by itself,
which of these was the case.

@@

%G3 ***DAN: check this again after Jasmin gets done making the new version of Fig. 5
Starting to fulfill goal G3 of the Introduction (to provide an empirical example of species coexistence 
which highlights the role ATAs can play), Fig. \ref{fig:fig5}a-c 
show that ATA contributions to coexistence often have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition, and that 
ATA rescue occurs for some combinations of parameters for this system (Fig. \ref{fig:fig5}a-c).

%***DAN: finish it once Jasmin finishes d-f
Plotting against two parameters at a time, Fig. \ref{fig:fig5}d-f show that...

@@

%***DAN: Jasmin, can you please ensure that ATA enclusion and rescue are 
%shaded and keyed in the legend for panels a-c in the same way as the earlier figures?
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig5.pdf}
\caption{ATA effects and ATA rescue and exclusion in the diatom system. 
The contribution of ATAs to the GWR of \emph{F. crotonensis}
in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
other components of the MCT decomposition (a-c). Panels a-c show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). 
For each panel, 
two of the three parameters defining the temperature oscillation (the amplitude, $a$; period, $P$; 
and mean, $\theta_0$; see Methods) were fixed at the values used by 
\cite{Descamps_2005} ($a=6^\circ$C, $P=60$d, $\theta_0=18^\circ$C), and 
GWR and components of the MCT decomposition
were plotted against the third parameter. The original values of the varying parameters 
are indicated by vertical dotted lines. 
%***DAN: Change the above sentence if Jasmin changes the font of the line
ATA contributions 
had magnitude comparable to other components, 
indicating that ATAs can contribute meaningfully
to diatom coexistence in this system. In some instances, the GWR line falls 
between the ATA line
and the horizontal axis, indicating that, for those parameter values, ATA rescue occurs. 
Standard errors of plotted quantities were always less then \Sexpr{round(se5,5)}, so are not shown.
For the parameters we considered, GWR of the other species, \emph{C. pseudostelligera}, 
was always positive both including and
excluding the effects of ATAs, so GWR for \emph{F. crotonensis}, decomposed here, is a 
sufficient coexistence metric.
%***DAN: Once Jasmin is done with the other part of the figure (the part that used to be Fig. 6), 
%finish this caption. Use the below caption, currently commented, to help. 
}  \label{fig:fig5}
\end{figure}

% \begin{figure}
% \includegraphics[width=.38\textwidth]{../results_figs/fig6.pdf}
% \caption{The contribution of ATAs to GWR of \emph{F. crotonensis}
% in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
% the GWR itself. The ratio $\Delta_i^{[EC]}/\text{GWR}$ is shown, larger magnitudes
% indicating greater importance of ATAs and values greater than $1$ corresponding to either
% ATA rescue or ATA exclusion (Methods). For this system and the plotted parameters, 
% $\Delta_i^{[EC]}$ was always positive, so cyan indicates exclusion of \emph{F. crotonensis} and
% magenta indicates coexistence of the two diatom species. Values greater than 1 or less than -1
% were remapped to 1 and -1, respectively, for readability.
% For the parameters we considered, GWR of the other species, \emph{C. pseudostelligera}, was always positive both including and
% excluding ATAs, so GWR for \emph{F. crotonensis} is a sufficient coexistence metric.
% Standard errors of plotted quantities were always less then \Sexpr{round(se6,5)}, so are not shown.} \label{fig:fig6}
% \end{figure}

### 2023-03-20 paper/SupMat.Rnw
commits I should have made a couple weeks ago

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3qij <- readRDS(file="../results_numeric/fig3qijmaxse.RDS")
@

@@

%***DAN: Jasmin, panels d-l of this figure are difficult to read because the y axis extent is such that
%you can't really see what any of the lines are doing except for the ditted and dot-dashed lines. I think we
%need to present 2 versions of the figure, this one and another one. For the other one, the y-axis limits 
%should be determined from the y axis extents of all the lines other than the dotted and dot-dashed lines. 
%Can you please mak this alternative version and let me know when it is made and what the pdf file is, so I 
%insert it? It is possible you will also need two versions of the figure below, but we won't know that 
%until you make that figure.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLNqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3qij,5)}, so are not displayed.}\label{fig:fig3_alt}
\end{figure}

@@

%***DAN: The code does not yet produce this figure. Eventually it needs to.
%NOTE: I have assumed this figure will look substantially the same as the corresponding main text 
%figure when I wrote the Results. If it does not, then some revisions will be needed.
\begin{figure}
%\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(0,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
\end{figure}

>>>>

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3qij <- readRDS(file="../results_numeric/fig3qijmaxse.RDS")
#se4qij <- readRDS(file="../results_numeric/fig4qijmaxse.RDS")
@

@@

%***DAN: Jasmin, please fix the collision of text that occurs in the text near the legend
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLNqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3qij,5)}, so are not displayed.}\label{fig:fig3_alt}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(0,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
\end{figure}
